A Comparision of Bootstrap Methods

### 2022-12-02 project/PaperTemplate/paper.Rmd
Added parallel

```{r setup, include = FALSE}
library(tidyverse)
library(mosaic)
library(mdsr)
library(knitr)
library(kableExtra)
library(boot)
library(gridExtra)
```

@@

```{r}
findCIs <- function(sampleinput, nboot) {

@@

```{r}
run_simulation_gamma <- function(num_reps, sample_size){
  set.seed(495)
  simulation_reps <- num_reps
  trueparameter <- 4
  n <- sample_size

  ci <- matrix(nrow = simulation_reps, ncol = 5)

  for (i in 1:simulation_reps){
    X <- rgamma(n, shape = 1, scale = 4)
    values <- data.frame(X)
    output <- findCIs(values, 2000)
    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
      trueparameter <= output$`Standard Interval`[2]
    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
      trueparameter <= output$`Percentile Interval`[2]
    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
      trueparameter <= output$`BC Interval`[2]
    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
      trueparameter <= output$`BCa Interval`[2]
    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
      trueparameter <= output$`Studentized Interval`[2]
  }

  ci_prop <- colSums(ci)/simulation_reps
  ci_prop
}

@@

```{r}
run_simulation_log_normal <- function(num_reps, sample_size){
  set.seed(495)
  simulation_reps <- num_reps
  trueparameter <- exp(1/2)
  n <- sample_size

  ci <- matrix(nrow = simulation_reps, ncol = 5)

  for (i in 1:simulation_reps){
    X <- rlnorm(n, meanlog = 0, sdlog = 1)
    values <- data.frame(X)
    output <- findCIs(values, 2000)
    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
      trueparameter <= output$`Standard Interval`[2]
    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
      trueparameter <= output$`Percentile Interval`[2]
    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
      trueparameter <= output$`BC Interval`[2]
    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
      trueparameter <= output$`BCa Interval`[2]
    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
      trueparameter <= output$`Studentized Interval`[2]
  }
  ci_prop <- colSums(ci)/simulation_reps
  ci_prop
}

@@

```{r}
run_simulation_normal <- function(num_reps, sample_size){
  set.seed(495)
  simulation_reps <- num_reps
  trueparameter <- 0
  n <- sample_size

  ci <- matrix(nrow = simulation_reps, ncol = 5)

  for (i in 1:simulation_reps){
    X <- rnorm(n, mean = 0, sd = 1)
    values <- data.frame(X)
    output <- findCIs(values, 2000)
    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
      trueparameter <= output$`Standard Interval`[2]
    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
      trueparameter <= output$`Percentile Interval`[2]
    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
      trueparameter <= output$`BC Interval`[2]
    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
      trueparameter <= output$`BCa Interval`[2]
    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
      trueparameter <= output$`Studentized Interval`[2]
  }
  ci_prop <- colSums(ci)/simulation_reps
  ci_prop
}

@@

```{r}
collect_data_gamma <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)

  simulation_reps <- sim_reps
  sample_sizes <- c(10, 25, 50, 100, 250)

  for (i in 1:5) {
    output2 <- run_simulation_gamma(simulation_reps, sample_sizes[i])
    data2[i, 1] <- sample_sizes[i]
    data2[i, 2:6] <- output2
  }

@@

```{r}
collect_data_log_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)

  simulation_reps <- sim_reps
  sample_sizes <- c(10, 25, 50, 100, 250)

  for (i in 1:5) {
    output2 <- run_simulation_log_normal(simulation_reps, sample_sizes[i])
    data2[i, 1] <- sample_sizes[i]
    data2[i, 2:6] <- output2
  }

@@

```{r}
collect_data_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)

  simulation_reps <- sim_reps
  sample_sizes <- c(10, 25, 50, 100, 250)

  for (i in 1:5) {
    output2 <- run_simulation_normal(simulation_reps, sample_sizes[i])
    data2[i, 1] <- sample_sizes[i]
    data2[i, 2:6] <- output2
  }

```{r, cache = TRUE}
set.seed(495)
gamma_data <- collect_data_gamma(30)
normal_data <- collect_data_normal(30)
log_normal_data <- collect_data_log_normal(30)
```

@@

```{r}
library(parallel)
numCores <- detectCores()
#simulation_reps <- 30
#simulation_rep <- seq(1,simulation_reps)
#sample_size <- 20
#  simulation_reps <- num_reps

run_simulation_normal1 <- function(simulation_rep){
  trueparameter <- 0

  collect_data_normal1 <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)

  sample_sizes = 10

  for (i in 1:5) {
    #output2 <- run_simulation_normal1(simulation_reps)
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_normal1, mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- colSums(df)/sim_reps

    xyzw <- collect_data_normal1(20)

>>>>

```{r setup, include = FALSE}
library(tidyverse)
library(mosaic)
library(mdsr)
library(knitr)
library(kableExtra)
library(boot)
library(gridExtra)
library(parallel)
```

@@

```{r find CIs}
findCIs <- function(sampleinput, nboot) {

@@

```{r run simulation gamma}
run_simulation_gamma <- function(simulation_rep){
  trueparameter <- 4

  X <- rgamma(sample_sizes, shape = 1, scale = 4)
  values <- data.frame(X)
  output <- findCIs(values, 2000)
  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
    trueparameter <= output$`Standard Interval`[2],
    trueparameter >= output$`Percentile Interval`[1] & 
    trueparameter <= output$`Percentile Interval`[2],
    trueparameter >= output$`BC Interval`[1] &
    trueparameter <= output$`BC Interval`[2],
    trueparameter >= output$`BCa Interval`[1] & 
    trueparameter <= output$`BCa Interval`[2],
    trueparameter >= output$`Studentized Interval`[1] & 
    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
  res <- rbind(data.frame(), ci)
  res
}

@@

```{r run simulation log normal}
run_simulation_log_normal <- function(simulation_rep){
  trueparameter <- exp(1/2)

  X <- rlnorm(sample_sizes, meanlog = 0, sdlog = 1)
  values <- data.frame(X)
  output <- findCIs(values, 2000)
  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
    trueparameter <= output$`Standard Interval`[2],
    trueparameter >= output$`Percentile Interval`[1] & 
    trueparameter <= output$`Percentile Interval`[2],
    trueparameter >= output$`BC Interval`[1] &
    trueparameter <= output$`BC Interval`[2],
    trueparameter >= output$`BCa Interval`[1] & 
    trueparameter <= output$`BCa Interval`[2],
    trueparameter >= output$`Studentized Interval`[1] & 
    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
  res <- rbind(data.frame(), ci)
  res
}

@@

```{r run simulation normal}
run_simulation_normal <- function(simulation_rep){
  trueparameter <- 0

@@

```{r collect data gamma}
collect_data_gamma <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 10
 # sim_reps <- 10
  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_gamma, mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

@@

```{r collect data log normal}
collect_data_log_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 10

  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_log_normal, mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

  log_normal_output <- as.data.frame(data2) %>% 
    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
  log_normal_output
}

```{r collect data normal}
collect_data_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 10

  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_normal, mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

@@

```{r, cache = TRUE}
set.seed(495)
gamma_data <- collect_data_gamma(5000)
normal_data <- collect_data_normal(5000)
log_normal_data <- collect_data_log_normal(5000)
```

@@
